GO

### 2020-03-28 analysis/12_GO.Rmd
GO working now

```{r bytissue}
hyp <- GO_DEGs %>% select(GO, starts_with("hyp"))
pit <- GO_DEGs %>% select(GO, starts_with("pit"))
gon <- GO_DEGs %>% select(GO, starts_with("gon"))

>>>>

```{r bytissue}
hyp <- GO_DEGs %>% select(GO, starts_with("male_hyp"), starts_with("female_hyp"))
pit <- GO_DEGs %>% select(GO, starts_with("male_pit"), starts_with("female_pit"))
gon <- GO_DEGs %>% select(GO, starts_with("male_gon"), starts_with("emale_gon"))
